---
title: "casestudy"
author: "linshan"
date: "2024-10-08"
output: github_document
---

```{r }
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis")

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

load the data
```{r}
library(p8105.datasets)
data(nyc_airbnb)
```

## Brainstorm questions
```{r}
summary(nyc_airbnb)
```

* Where are the max and min airbnb prices?\
```{r}
max(nyc_airbnb$price)
min(nyc_airbnb$price)
```
* Where are average prices?\
`r mean(nyc_airbnb$price)`
* What's the relationship between number of reviews and average review?\
* Does room type affect availability?\
* What's the location of the unit?\
 * What areas are popular?\
 * Popularity = number of units? Average price?\
* Are there repeat hosts?\
 * If so, what does that mean?\
 看看有多少人有不止一个airbnb
```{r}
nyc_airbnb %>%
  filter(calculated_host_listings_count > 5) %>%
  distinct(host_id, host_name, calculated_host_listings_count)
```

计算不同地区的不同公寓类型的平均价格
```{r}
nyc_airbnb |>
  group_by(neighbourhood_group,room_type) |>
  summarize(mean_price = mean(price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```
看不同房间类型的价格 histogram
```{r}
nyc_airbnb |>
  ggplot(aes(x = price, fill = room_type)) +
  geom_histogram(position = "dodge") +
  scale_x_continuous(limits = c(0, 250))
```
review score和公寓价格之间的关系？？

```{r}
nyc_airbnb |>
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", 
         price < 1000,
         room_type == "Entire home/apt") |>
  mutate(neighbourhood = fct_reorder(neighbourhood,price)) |>
  ggplot(aes(x = neighbourhood, y = price , color = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) #坐标轴标注倾斜
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", 
         price < 1000,
         room_type == "Entire home/apt") |>
  group_by(neighbourhood) |>
  summarize(mean_price = mean(price)) |>
  arrange(desc(mean_price))
```

try leaflet
```{r}
library(leaflet)
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", 
         price < 1000) |>
  slice(100) |>
  leaflet() |>
  addTiles() |>
  addMarkers(~ lat, ~ long)
```








